The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-01 Writeup/paper_v3.tex
Multiply defined label 2Dhist fixed
updated mn2e bst file
add Euclid ref

\begin{document}
\bibliographystyle{plainnat}
\maketitle

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of $M_\text{F814W}$ for various flux-limited samples are plotted together. The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
   \label{fig:2Dhist}
 \end{figure}

@@

At $M_\text{F814W}\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit. We obtain 97.84\% completeness in this bin for $M_\text{F814W}$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
Thus the sample $z\le1$ and $M_\text{F814W}<-22$ is at least 97.84\% complete. Fig.~\ref{fig:2Dhist} shows that at $M_\text{F814W}<-22$, we are not affected by flux limit yet.

@@

Our result has serious implications for realistic image simulations for Weak Lensing. 
It suggests that the training sample is affected by cosmic variance so as to possibly bias the conclusions from the simulations. 
This is particularly a problem with narrow surveys where a single galaxy cluster or a void could affect the environment significantly. 
Thus, we are forced to use wider redshift bins, much larger than the uncertainties in the redshifts, so as to be able to wash out the environmental dependence.
However, future surveys such as the Large Synoptic Survey Telescope\citep[LSST;][]{LSST} will image larger areas of sky mitigating the dependence of local environment in image simulations.

>>>>

\begin{document}
\bibliographystyle{mn2e2}
\maketitle

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of $M_\text{F814W}$ for various flux-limited samples are plotted together. The vertical line corresponds to the luminosity cut of $-20.8$, below which the $m_\text{F814W}<23.5$ sample has 95.3\% of the galaxies in the $m_\text{F814W}<25.2$ sample.}
   \label{fig:MIhist}
 \end{figure}

@@

At $M_\text{F814W}\sim-22.0$, we see the sample is beginning to be biased in the $0.9<z<1.0$ bin due to the flux limit. We obtain 97.84\% completeness in this bin for $M_\text{F814W}$, where completeness is defined as the ratio between the number of galaxies in $m_\text{F814W}\le 23.5$ and in $m_\text{F814W}\le25.2$ samples.
Thus the sample $z\le1$ and $M_\text{F814W}<-22$ is at least 97.84\% complete. Figs.~\ref{fig:2Dhist} \&~\ref{fig:MIhist} show that at $M_\text{F814W}<-22$, we are not affected by flux limit yet.

@@

Our result has serious implications for realistic image simulations for Weak Lensing. 
It suggests that the training sample is affected by cosmic variance so as to possibly bias the conclusions from the simulations. 
This is particularly a problem with narrow surveys where a single galaxy cluster or a void could affect the environment significantly. 
Thus, we are forced to use wider redshift bins, much larger than the uncertainties in the redshifts, so as to be able to wash out the environmental dependence.
However, future surveys such as the Large Synoptic Survey Telescope\citep[LSST;][]{LSST_Book} will image larger areas of sky mitigating the dependence of local environment in image simulations.
